\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-09-13 paper.tex
update

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. We then define the rotation $R$ using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  In the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
  \begin{align}
    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
  \end{align}
  with $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
\end{definition}

@@

\subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$. The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$. This constraint can be written as,

@@

  For cases where $q_{avoid} \notin \cE(q(t_2),q(t_1),r)$, $\pi_{p\cE}(q_{avoid}) = q_{avoid}$. And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse.

  \zyang{can this be treated as proposition}
  \begin{proposition} \label{prop:ellipse-project-canonical}
  In canonical frame $\cF_{\cE}$, the projection from a point $q^{\cE}_{avoid}\in \cE$ inside the ellipse to the boundary of $\cE$:
  \begin{equation}
  	q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
  \end{equation}
  %where $S=(I+sQ)\inverse$.Using the fact that since $q^\cE_p$ is a point on the ellipse, 
  where $s$ can be solved as the root of the equation obtained by substituting \eqref{eq:qp from S} in $\Eframe E(\Eframe q)$:
  \begin{equation}
    0=F(s)={q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1,
  \end{equation}
  where
  \begin{equation}
    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
  \end{equation}
 Detailed methods for computing $s$ can be found in \cite{eberly}. 
  \end{proposition}
  \begin{proof}
  Proof can be found in Appendix~\Cref{proof:ellipse-project-canonical}
  \end{proof}

  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
  % \begin{equation}
  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
  % \end{equation}

@@

  \begin{proposition}\label{prop:Ellipse2PointDiff}
    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (where we use $q$ as a shorthand notation for $q^\cE_{avoid}$)
    \begin{multline}
      \partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} \pi_{p\cE}=-2 H [ SH(q-o)]_{\times}U   \\
      + \left( (q\transpose \partial_sQ' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q - o]_\times U \right. \\
      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o
    \end{multline}
  \end{proposition}
  The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{Ellipse2line_V2}
\caption{Plane-ellipse constraint. Projected a ellipsoid to one side of a plane. The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
\label{fig:Ellipse-to-plane}
\end{center}
\end{figure}

For a intermediate step to get the relationship between a polygon shaped forbidden region, we first consider a forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
  Using the transformation introduced in (\ref{sec:rotation2Standard}), the ellipse can be transferred into a standard one with the new hyperplane in the form of $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n
\end{equation}
\begin{equation} 
	d_\cE =-\vn\transpose o + d
  \end{equation}
\subsubsection{Projection via the tangent interpolation point}
  For each $\cL_\cE$, there exist two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse, where
  \begin{equation}
    d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}.
  \end{equation}
  The corresponding tangent points are given as 
  \begin{equation}
    p^\cE_{1} = \frac{  d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},
  \end{equation}
  \begin{equation}
   p^\cE_{2} = -  p^\cE_{1}.
  \end{equation}
  \rtron{Refer to figure}
  We use these two tangent points to define a novel measure of displacement between a plane and an ellipse.
  \begin{definition}
    The \emph{tangent interpolation point} is defined as 
    \begin{equation}\label{equ:ProjectPoint}
      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}
    \end{equation}
  \end{definition}
  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively. 
  % it is easy to see that $\Eframe p_{\cL} \in \mathcal{L}$, and $p_{\mathcal{L}}$ can be used to indicate the relationship between the $\mathcal{L}$ and $\mathcal{E}$, which is shown below. \zyang{how to emphaise this? maybe a graph here?}
  %The reason such that a specific point is used is for the convenience of evaluating ellipse-plane-segment relationship in Section~\ref{chapter:ellipse to segment}.
  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint. Using this fact, we define the following projection operator:
  \begin{equation}\label{equ:plane2ellipse}
    \pi^\cE_{\vn \cE}(q) =\begin{cases}
      p^\cE_{t1}-p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
      p^\cE_{t2}-p^\cE_{\cL} &  d_\cE \in [- d_{\cE t},0), \\
      {0} & \textrm{otherwise}.
    \end{cases}
  \end{equation}
  \subsubsection{ADMM constraints}
  Transforming the projection $\pi^\cE$ back to $\cF$ we have:
  \begin{equation}\label{equ:constraint plane to ellipse}
    D_{\vn}(q)= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o,
  \end{equation}
  with the corresponding constraint written as
  \begin{equation}
    \zeta_\vn = \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \}
  \end{equation}
  \begin{equation}
   \quad\Pi_\vn(D_{\vn}(q)) = {0}
  \end{equation}

  \subsubsection{Gradients for the projection function}
  \begin{proposition}\label{prop:dpi_ne dt}
    The differential of the projection function $\Eframe \Pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  Based on the previous proposition, the differential of (\ref{equ:constraint plane to ellipse}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

To avoid (or stay in) a region defined by several hyperplanes, the relative position between the ellipse and segment of the hyperplane needs to be studied instead of the whole plane. Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
\begin{equation}
\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
\end{equation}
And using the $p_{\cL}$ defined in (\ref{equ:ProjectPoint}), we define
\begin{equation}
D_{seg}(q) = \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & otherwise
\end{cases}
\end{equation}
where $D_{p\cE}$ and $D_{\vn\cE}$ are corresponding constraint function introduced in section \ref{sec:ellipsoid-point} and \ref{sec:ellipsoide-plane}
with the constraint set and projection written as:
\begin{equation}
\zeta_{seg} = \{q\in\mathbb{R}^{nm}:\norm{D_{seg}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{seg}(D_{seg}(q)) = {0}
\end{equation}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. And a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) is also added to prevent cases where the ellipse is a subset of the region. Similar to \eqref{equ:ProjectPoint}, we define
\begin{equation}
D_{cp}(q) = \bmat{D_{seg1}\\D_{seg2}\\ \vdots}
\end{equation}
with the constraint set and projection written as:
\begin{equation}
\zeta_{cp} = \{q\in\mathbb{R}^{nm}:\norm{D_{cp}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{cp}(D_{cp}(q)) = {0}
\end{equation}

@@

To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtronref{refer to introductory figure}. 
These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs. 
Note that \emph{cross-trajectory co-observation}, are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised. \rtronref{(More discussion in Sec. ??)}.

@@

\subsection{Rapidly-exploring Random Trees}
In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method). \rtronhl{Move to the end of this RRT* section}{Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths. While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section. RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.}

@@

  \subsection{Proof of proposition \ref{prop:dpi_ne dt}}\label{proof:dpi_ne dt}
    We first need to derive $\dot{d}_\cE$ and $\dot{d}_{\cE t}$

@@

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC}
}

>>>>

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. We then define the rotation $R$ using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  In the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
  \begin{align}
    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
  \end{align}
  with $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
  And the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
   \begin{equation}
     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
     \end{equation}
\end{definition}

@@

\subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
\zyang{change this to a circle by adding radius to projection?}
As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$. The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$. This constraint can be written as,

@@

  For cases where $q_{avoid} \notin \cE(q(t_2),q(t_1),r)$, $\pi_{p\cE}(q_{avoid}) = q_{avoid}$. And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse. In canonical frame $\cF_{\cE}$, the projected point $q^{\cE}_{p}$ can be written as:
  \begin{equation}
  	q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
  \end{equation}
  %where $S=(I+sQ)\inverse$.Using the fact that since $q^\cE_p$ is a point on the ellipse, 
  where $s$ can be solved as the root of the \eqref{equ:standard-ellipse}:
  \begin{equation}
    {q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1=0
  \end{equation}
  where
  \begin{equation}
    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
  \end{equation}
 Detailed methods for computing $s$ can be found in \cite{yang2021multi} \cite{yang2020multi} \cite{eberly}.

@@

  \begin{proposition}\label{prop:Ellipse2PointDiff}
    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (where we use $q$ as a shorthand notation for $q^\cE_{avoid}$)
    \begin{multline}
      \partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} \pi_{p\cE}=-2 H [ SH(q-o)]_{\times}U   \\
      + \left( (q\transpose \partial_sQ' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q - o]_\times U \right. \\
      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o
    \end{multline}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:Ellipse2PointDiff}.
  \end{proof}
  The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
\caption{Plane-ellipse constraint. Projected a ellipsoid to one side of a plane. The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
\label{fig:Ellipse-to-plane}
\end{center}
\end{figure}

For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d
\end{equation}
The corresponding constraint can be written as:

\begin{constraint}[Plane-ellipsoid reachability constraint]
\begin{align}
D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
   \Pi_\sZ(z) & = \overrightarrow{0}, 
\end{align}
\end{constraint}
where $\pi^\cE_{\vn \cE}(q)$ is the projection operator defined as:
  \begin{equation}\label{equ:plane2ellipse}
    \pi^\cE_{\vn \cE}(q) =\begin{cases}
      p^\cE_{t1}-p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
      p^\cE_{t2}-p^\cE_{\cL} &  d_\cE \in [- d_{\cE t},0), \\
      {0} & \textrm{otherwise}.
    \end{cases}
  \end{equation}
$p^{\cE}_{1}$ and $p^{\cE}_{2}$ are tangent points on two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse (\Cref{fig:Ellipse-to-plane}), defined as 
 \begin{equation}
    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
  \end{equation}
where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$. And the \emph{tangent interpolation point} is defined as 
    \begin{equation}\label{equ:ProjectPoint}
      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
    \end{equation}
  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.

  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\Eframe \pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
\begin{equation}
\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
\end{equation}
And using the $p_{\cL}$ defined in (\ref{equ:ProjectPoint}), we define
\begin{equation}
D_{seg}(q) = \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & otherwise
\end{cases}
\end{equation}
where $D_{p\cE}$ and $D_{\vn\cE}$ are corresponding constraint function introduced in section \ref{sec:ellipsoid-point} and \ref{sec:ellipsoide-plane}
with the constraint set and projection written as:
\begin{equation}
\zeta_{seg} = \{q\in\mathbb{R}^{nm}:\norm{D_{seg}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{seg}(D_{seg}(q)) = {0}
\end{equation}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. And a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) is also added to prevent cases where the ellipse is a subset of the region. Similar to \eqref{equ:ProjectPoint}, we define
\begin{equation}
D_{cp}(q) = \bmat{D_{seg1}\\D_{seg2}\\ \vdots}
\end{equation}
with the constraint set and projection written as:
\begin{equation}
\zeta_{cp} = \{q\in\mathbb{R}^{nm}:\norm{D_{cp}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{cp}(D_{cp}(q)) = {0}
\end{equation}

@@

To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtron{refer to introductory figure}. 
These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs. 
Note that \emph{cross-trajectory co-observation}, are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised. \rtron{(More discussion in Sec. ??)}.

@@

\subsection{Rapidly-exploring Random Trees}
In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method). \rtronhl{Move to the end of this RRT* section} Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths. While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section. RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.

@@

  \subsection{Proof of proposition \ref{prop:dpi_ne_dt}}\label{proof:dpi_ne_dt}
    We first need to derive $\dot{d}_\cE$ and $\dot{d}_{\cE t}$

@@

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC,tron,ziqi}
}
